Experience-Biased Symbolic Planning

### 2014-05-16 AAAI_AuthorKit/paper.tex
Morning submission

@@

\begin{table}
	\centering
	\resizebox{\columnwidth}{!}{%
	    \begin{tabular}{| r | c | c | c | c |}
	    \hline
	    Domain & Inst & 5 steps & 20 steps & 50 steps
	    \\ \hline
	    blocks & 35 & 2.12-7.92 & 2.12-8.70 & 2.21-6.25
	    \\ 
	    driverlog & 14 & 0.86-2.42 & 0.85-1.30 & 0.82-1.20
	    \\ 
	    elevators & 30 & 1.09-4.04 & 0.99-2.76 & 0.90-2.06
	    \\ 
	    grid & 2 & 2.21-3.71 & 1.11-1.34 & 1.10-1.30
	    \\ 
	    logistics00 & 28 & 1.00-1.15 & 0.90-1.11 & 0.84-1.18
	    \\ 
	    logistics98 & 5 & 1.01-2.95 & 0.82-2.06 & 0.80-2.41
	    \\ 
	    pipesworld-notankage & 15 & 1.09-5.30 & 1.00-5.46 & 1.00-2.88
	    \\ 
	    pipesworld-tankage & 8 & 1.00-1.20 & 0.99-1.00 & 1.00-1.13
	    \\ 
	    rovers & 13 & 1.00-1.50 & 1.00-1.00 & 1.00-1.00
	    \\ 
	    satellite & 16 & 0.91-1.25 & 0.87-1.15 & 0.90-1.43
	    \\ 
	    scananalyzer & 16 & 0.74-1.52 & 1.00-1.00 & 1.00-1.00
	    \\ 
	    transport & 23 & 1.26-1.91 & 0.93-1.87 & 0.98-1.46
	    \\ 
	    zenotravel & 13 & 0.80-1.27 & 0.84-1.02 & 1.00-1.00
	    \\ \hline
	    TOTAL & 218 & 0.99-2.72 & 1.00-2.07 & 1.00-1.88
	    \\ \hline
	    \end{tabular}%
	}
	\caption{Experiment 2 speedup statistics, summarized in the form (1st quartile)-(3rd quartile).}
	 \label{tab:walk}
\end{table}

@@

\begin{figure}
	\centering
	\includegraphics[scale=0.5]{Speedup_20_0.png}
	\caption{Speedups when planning with 20\% of the control experience, displaced 0 steps from the control query.}
	 \label{fig:s_20_0}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[scale=0.5]{Speedup_100_50.png}
	\caption{Speedups when planning with 100\% of the control experience, displaced 50 steps from the control query.}
	 \label{fig:s_100_50}
\end{figure}

We saw that, by reusing pieces from past plans, E-Graph-based planners can find solutions more quickly as they learn and acquire experiences. Many interesting directions remain for future investigation. It remains unclear how the bias parameters should be set. In addition, more advanced schemes will be needed to expand and prune E-Graphs if they grow large from collecting a lot of solutions. Keeping track of the most recently computed plans seems like a good idea intuitively, but other possibilities may be worth trying.

As mentioned in the discussion, generalization and parallelization certainly merit further investigation. Generalization is a particularly important problem in AI learning theory, and there is plenty of literature on the topic. For example, \cite{fikes1972learning} generalize plans on the original STRIPS problem solver. The problem of generalization seems related to that of abstraction, or automatically extracting structural information from a symbolic domain or problem description. Works such as \cite{helmert2007flexible} project symbolic state graphs onto smaller spaces; one could potentially apply E-graphs on the projected space to achieve the desired generalization.

@@

Finally, E-Graphs might find other uses, such as in replanning. If an unexpected event invalidates a robot's plan mid-execution, the replanner can recall the original solution as an E-Graph to encourage reparations along the old path. In addition to speeding up replanning, the E-Graph could result in a less disruptive solution, in the sense that it avoids unnecessarily deviating from the original plan. Minimizing disruption is important when resources must be allocated in advance according to the plan, or when cognitively-burdened humans are involved with its execution.

>>>>

\begin{table}
	\centering
	\resizebox{\columnwidth}{!}{%
	    \begin{tabular}{| r | c | c | c | c |}
	    \hline
	    Domain & Count & 5 steps & 20 steps & 50 steps
	    \\ \hline
	    blocks & 35 & 2.12-7.92 & 2.12-8.70 & 2.21-6.25
	    \\ 
	    driverlog & 14 & 0.86-2.42 & 0.85-1.30 & 0.82-1.20
	    \\ 
	    elevators & 30 & 1.09-4.04 & 0.99-2.76 & 0.90-2.06
	    \\ 
	    grid & 2 & 2.21-3.71 & 1.11-1.34 & 1.10-1.30
	    \\ 
	    logistics00 & 28 & 1.00-1.15 & 0.90-1.11 & 0.84-1.18
	    \\ 
	    logistics98 & 5 & 1.01-2.95 & 0.82-2.06 & 0.80-2.41
	    \\ 
	    pipesworld-notankage & 15 & 1.09-5.30 & 1.00-5.46 & 1.00-2.88
	    \\ 
	    pipesworld-tankage & 8 & 1.00-1.20 & 0.99-1.00 & 1.00-1.13
	    \\ 
	    rovers & 13 & 1.00-1.50 & 1.00-1.00 & 1.00-1.00
	    \\ 
	    satellite & 16 & 0.91-1.25 & 0.87-1.15 & 0.90-1.43
	    \\ 
	    scananalyzer & 16 & 0.74-1.52 & 1.00-1.00 & 1.00-1.00
	    \\ 
	    transport & 23 & 1.26-1.91 & 0.93-1.87 & 0.98-1.46
	    \\ 
	    zenotravel & 13 & 0.80-1.27 & 0.84-1.02 & 1.00-1.00
	    \\ \hline
	    TOTAL & 218 & 0.99-2.72 & 1.00-2.07 & 1.00-1.88
	    \\ \hline
	    \end{tabular}%
	}
	\caption{Experiment 2 speedup statistics, summarized in the form (1st quartile)-(3rd quartile).}
	 \label{tab:walk}
\end{table}

@@

@@

We saw that, by reusing pieces from past plans, E-Graph-based planners can find solutions more quickly as they learn and acquire experiences. Many interesting directions remain for future investigation. It remains unclear how the bias parameters should be set. In addition, more advanced schemes will be needed to expand and prune E-Graphs if they grow large from collecting a lot of solutions. Keeping track of the most recently computed plans seems like a good idea intuitively, but other possibilities may be worth trying.
\begin{figure}
	\centering
	\includegraphics[scale=0.5]{Speedup_20_0.png}
	\caption{Speedups when planning with 20\% of the control experience, displaced 0 steps from the control query.}
	 \label{fig:s_20_0}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[scale=0.5]{Speedup_100_50.png}
	\caption{Speedups when planning with 100\% of the control experience, displaced 50 steps from the control query.}
	 \label{fig:s_100_50}
\end{figure}
As mentioned in the discussion, generalization and parallelization certainly merit further investigation. Generalization is a particularly important problem in AI learning theory, and there is plenty of literature on the topic. For example, \cite{fikes1972learning} generalize plans on the original STRIPS problem solver. The problem of generalization seems related to that of abstraction, or automatically extracting structural information from a symbolic domain or problem description. Works such as \cite{helmert2007flexible} project symbolic state graphs onto smaller spaces; one could potentially apply E-graphs on the projected space to achieve the desired generalization.

@@

Finally, E-Graphs might find other uses, such as in replanning. If an unexpected event invalidates a robot's plan mid-execution, the replanner can recall the original solution as an E-Graph to encourage reparations along the old path. In addition to speeding up replanning, the E-Graph could result in a less disruptive solution, in the sense that it avoids unnecessarily deviating from the original plan. Minimizing disruption is important when resources must be allocated in advance according to the plan, or when cognitively burdened humans are involved with its execution.
